---
title: "Plots"
author: "Abraham Iñiguez"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Packages

```{r message = FALSE}
package.list = c("ggplot2","tidyr", "ggridges",
                 "patchwork")
  sapply(package.list, function(package){
  if(!require(package, character.only = TRUE)){
  install.packages(package, dependencies = TRUE)
} 
  library(package, character.only = TRUE)
})
# packages = c("ggplot2", "tidyr", "ggridges")
# invisible(lapply(packages, library, character.only = TRUE))

```

## Local Metrics Plots

#### Strength (Redundancy) \|Psych Version\|

```{r}

# Data frame with strength deltas (Redundant - True)
sdeltas = data.frame(
  Strength = local_metrics[, (nv + 1):(2*nv), "Strength"] - local_metrics[, 1:nv, "Strength"],
  Strength.wo = local_metrics[, (nv + 1):(2*nv), "Strength w/o Clone"] - local_metrics[, 1:nv, "Strength w/o Clone"]
)

# Rename columns of data frame
colnames(sdeltas) = c(paste0("P", 1:(nv-1)), "Target", paste0("P", 1:(nv-1), ".wo"), "Target.wo")

# Convert to long data frame
sdeltas.long = pivot_longer(sdeltas, cols = c(paste0("P", 1:(nv-1)), "Target", paste0("P", 1:(nv-1), ".wo"), "Target.wo"))

# Rename columns of long data frame
colnames(sdeltas.long) = c("Node", "Strength.Delta")

# Factor variable "Node"
sdeltas.long$Node = factor(sdeltas.long$Node, levels = c(paste0("P", 1:(nv-1)), "Target", paste0("P", 1:(nv-1), ".wo"), "Target.wo"))

# Use tapply() to obtain measures of central tendency
mean.sdeltas = tapply(X = sdeltas.long$Strength.Delta, INDEX = sdeltas.long$Node, FUN = mean)
sd.sdeltas = tapply(X = sdeltas.long$Strength.Delta, INDEX = sdeltas.long$Node,FUN = sd)


# Data frame ready for ggplot 
sdeltas.gg = data.frame(
  Node = names(mean.sdeltas),
  Mean = as.vector(mean.sdeltas),
  SE = (as.vector(sd.sdeltas))/sqrt(1000))

# Add grouping column for fill and color

sdeltas.gg$Type = c(rep("With Clone", nv), rep("Without Clone", nv))

# Match using gsub() any node that ends with ".wo" and remove for ggplot

sdeltas.gg$Node = gsub("\\.wo$", "", sdeltas.gg$Node)

# Plot using ggplot2

jpeg("/Users/abraham/Library/CloudStorage/Box-Box/Redundancy_Project/Output/Delta Strength Plot (Redundancy).jpg",
     width= 12,
     height= 6,
     res=800,
     units="in")
ggplot(sdeltas.gg, aes(x = Node, y = Mean, shape = Node)) +
  geom_point(size = 5, aes(fill = Type, color = Type), 
             alpha = .8, show.legend = TRUE) +
  scale_shape_manual(values = c("P1" = 21, "P2" = 22, "P3" = 23, "Target" = 24)) +
  geom_errorbar(aes(ymin = Mean - SE, ymax = Mean + SE), linewidth = .25, width = .15) +
  ylim(-.5, .5) +
  labs(x = "Node",
       y = expression(paste(Delta, " Strength"))) +
  geom_hline(yintercept = 0,
             linetype = 2,
             color = "red") +
  
  theme_minimal(base_size = 20) +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 8),
        legend.background = element_rect(color = "lightgrey"),
        legend.spacing.y = unit(1, "cm")) +
  guides(fill = guide_legend(byrow = TRUE),
         shape = guide_legend(byrow = TRUE,
                              override.aes = list(size = 4)))
dev.off()
```

### Expected Influence (Redundancy)

```{r}
# Data frame with Expected Influence deltas (Redundant - True)
eideltas = data.frame(
  Expected.Influence = local_metrics[, (nv + 1):(2*nv), "Expected Influence"] - local_metrics[, 1:nv, "Expected Influence"],
  Expected.Influence.wo = local_metrics[, (nv + 1):(2*nv), "Expected Influence w/o Clone"] - local_metrics[, 1:nv, "Expected Influence w/o Clone"]
)

# Rename columns of data frame
colnames(eideltas) = c(paste0("P", 1:(nv-1)), "Target", paste0("P", 1:(nv-1), ".wo"), "Target.wo")

# Convert to long data frame
eideltas.long = pivot_longer(eideltas, cols = c(paste0("P", 1:(nv-1)), "Target", paste0("P", 1:(nv-1), ".wo"), "Target.wo"))

# Rename columns of long data frame
colnames(eideltas.long) = c("Node", "Expected.Influence.Delta")

# Factor variable "Node"
eideltas.long$Node = factor(eideltas.long$Node, levels = c(paste0("P", 1:(nv-1)), "Target", paste0("P", 1:(nv-1), ".wo"), "Target.wo"))

# Remove NAs, as there were 4 
eideltas.long = na.omit(eideltas.long)
head(eideltas.long)
# Use tapply() to obtain measures of central tendency
mean.eideltas = tapply(X = eideltas.long$Expected.Influence.Delta, INDEX = eideltas.long$Node, FUN = mean)
sd.eideltas = tapply(X = eideltas.long$Expected.Influence.Delta, INDEX = eideltas.long$Node,FUN = sd)


# Data frame ready for ggplot 
eideltas.gg = data.frame(
  Node = names(mean.eideltas),
  Mean = as.vector(mean.eideltas),
  SE = (as.vector(sd.eideltas))/sqrt(1000))

# Add grouping column for fill and color

eideltas.gg$Type = c(rep("With Clone", nv), rep("Without Clone", nv))

# Match using gsub() any node that ends with ".wo" and remove for ggplot

eideltas.gg$Node = gsub("\\.wo$", "", eideltas.gg$Node)

# Plot using ggplot2

jpeg("/Users/abraham/Library/CloudStorage/Box-Box/Redundancy_Project/Output/Delta Expected Influence Plot (Redundancy).jpg",
     width= 12,
     height= 6,
     res=800,
     units="in")
ggplot(eideltas.gg, aes(x = Node, y = Mean, shape = Node)) +
  geom_point(size = 5, aes(fill = Type, color = Type), 
             alpha = .8, show.legend = TRUE) +
  scale_shape_manual(values = c("P1" = 21, "P2" = 22, "P3" = 23, "Target" = 24)) +
  geom_errorbar(aes(ymin = Mean - SE, ymax = Mean + SE), linewidth = .25, width = .15) +
  ylim(-.5, .5) +
  labs(x = "Node",
       y = expression(paste(Delta, " Expected Influence"))) +
  geom_hline(yintercept = 0,
             linetype = 2,
             color = "red") +
  
  theme_minimal(base_size = 20) +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 8),
        legend.background = element_rect(color = "lightgrey"),
        legend.spacing.y = unit(1, "cm")) +
  guides(fill = guide_legend(byrow = TRUE),
         shape = guide_legend(byrow = TRUE,
                              override.aes = list(size = 4)))
dev.off()
```

### Closeness (Redundancy)

```{r}

# Data frame with closeness deltas (Redundant - True)
cdeltas = data.frame(
  Closeness = local_metrics[, (nv + 1):(2*nv), "Closeness"] - local_metrics[, 1:nv, "Closeness"],
  Closeness.wo = local_metrics[, (nv + 1):(2*nv), "Closeness w/o Clone"] - local_metrics[, 1:nv, "Closeness w/o Clone"]
)

# Rename columns of data frame
colnames(cdeltas) = c(paste0("P", 1:(nv-1)), "Target", paste0("P", 1:(nv-1), ".wo"), "Target.wo")

# Convert to long data frame
cdeltas.long = pivot_longer(cdeltas, cols = c(paste0("P", 1:(nv-1)), "Target", paste0("P", 1:(nv-1), ".wo"), "Target.wo"))

# Rename columns of long data frame
colnames(cdeltas.long) = c("Node", "Closeness.Delta")

# Factor variable "Node"
cdeltas.long$Node = factor(cdeltas.long$Node, levels = c(paste0("P", 1:(nv-1)), "Target", paste0("P", 1:(nv-1), ".wo"), "Target.wo"))

# Remove NAs, as there were 4 
cdeltas.long = na.omit(cdeltas.long)

# Use tapply() to obtain measures of central tendency
mean.cdeltas = tapply(X = cdeltas.long$Closeness.Delta, INDEX = cdeltas.long$Node, FUN = mean)
sd.cdeltas = tapply(X = cdeltas.long$Closeness.Delta, INDEX = cdeltas.long$Node,FUN = sd)


# Data frame ready for ggplot 
cdeltas.gg = data.frame(
  Node = names(mean.cdeltas),
  Mean = as.vector(mean.cdeltas),
  SE = (as.vector(sd.cdeltas))/sqrt(1000))

# Add grouping column for fill and color

cdeltas.gg$Type = c(rep("With Clone", nv), rep("Without Clone", nv))

# Match using gsub() any node that ends with ".wo" and remove for ggplot

cdeltas.gg$Node = gsub("\\.wo$", "", cdeltas.gg$Node)

# Plot using ggplot2

jpeg("/Users/abraham/Library/CloudStorage/Box-Box/Redundancy_Project/Output/Delta Closeness Plot (Redundancy).jpg",
     width= 12,
     height= 6,
     res=800,
     units="in")
ggplot(cdeltas.gg, aes(x = Node, y = Mean, shape = Node)) +
  geom_point(size = 5, aes(fill = Type, color = Type), 
             alpha = .8, show.legend = TRUE) +
  scale_shape_manual(values = c("P1" = 21, "P2" = 22, "P3" = 23, "Target" = 24)) +
  geom_errorbar(aes(ymin = Mean - SE, ymax = Mean + SE), linewidth = .25, width = .15) +
  ylim(-.5, .5) +
  labs(x = "Node",
       y = expression(paste(Delta, " Closeness"))) +
  geom_hline(yintercept = 0,
             linetype = 2,
             color = "red") +
  
  theme_minimal(base_size = 20) +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 8),
        legend.background = element_rect(color = "lightgrey"),
        legend.spacing.y = unit(1, "cm")) +
  guides(fill = guide_legend(byrow = TRUE),
         shape = guide_legend(byrow = TRUE,
                              override.aes = list(size = 4)))
dev.off()
```

### Betweenness (Redundancy)

```{r}
# Data frame with Betweenness deltas (Redundant - True)
bdeltas = data.frame(
  Betweenness = local_metrics[, (nv + 1):(2*nv), "Betweenness"] - local_metrics[, 1:nv, "Betweenness"],
  Betweenness.wo = local_metrics[, (nv + 1):(2*nv), "Betweenness w/o Clone"] - local_metrics[, 1:nv, "Betweenness w/o Clone"]
)

# Rename columns of data frame
colnames(bdeltas) = c(paste0("P", 1:(nv-1)), "Target", paste0("P", 1:(nv-1), ".wo"), "Target.wo")

# Convert to long data frame
bdeltas.long = pivot_longer(bdeltas, cols = c(paste0("P", 1:(nv-1)), "Target", paste0("P", 1:(nv-1), ".wo"), "Target.wo"))

# Rename columns of long data frame
colnames(bdeltas.long) = c("Node", "Betweenness.Delta")

# Factor variable "Node"
bdeltas.long$Node = factor(bdeltas.long$Node, levels = c(paste0("P", 1:(nv-1)), "Target", paste0("P", 1:(nv-1), ".wo"), "Target.wo"))

# Remove NAs, as there were 4 
bdeltas.long = na.omit(bdeltas.long)

# Use tapply() to obtain measures of central tendency
mean.bdeltas = tapply(X = bdeltas.long$Betweenness.Delta, INDEX = bdeltas.long$Node, FUN = mean)
sd.bdeltas = tapply(X = bdeltas.long$Betweenness.Delta, INDEX = bdeltas.long$Node,FUN = sd)


# Data frame ready for ggplot 
bdeltas.gg = data.frame(
  Node = names(mean.bdeltas),
  Mean = as.vector(mean.bdeltas),
  SE = (as.vector(sd.bdeltas))/sqrt(1000))

# Add grouping column for fill and color

bdeltas.gg$Type = c(rep("With Clone", nv), rep("Without Clone", nv))

# Match using gsub() any node that ends with ".wo" and remove for ggplot

bdeltas.gg$Node = gsub("\\.wo$", "", bdeltas.gg$Node)

# Plot using ggplot2

jpeg("/Users/abraham/Library/CloudStorage/Box-Box/Redundancy_Project/Output/Delta Betweenness Plot (Redundancy).jpg",
     width= 12,
     height= 6,
     res=800,
     units="in")
ggplot(bdeltas.gg, aes(x = Node, y = Mean, shape = Node)) +
  geom_point(size = 5, aes(fill = Type, color = Type), 
             alpha = .8, show.legend = TRUE) +
  scale_shape_manual(values = c("P1" = 21, "P2" = 22, "P3" = 23, "Target" = 24)) +
  geom_errorbar(aes(ymin = Mean - SE, ymax = Mean + SE), linewidth = .25, width = .15) +
  ylim(-.5, .5) +
  labs(x = "Node",
       y = expression(paste(Delta, " Betweenness"))) +
  geom_hline(yintercept = 0,
             linetype = 2,
             color = "red") +
  
  theme_minimal(base_size = 20) +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "right",
        legend.direction = "vertical",
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 8),
        legend.background = element_rect(color = "lightgrey"),
        legend.spacing.y = unit(1, "cm")) +
  guides(fill = guide_legend(byrow = TRUE),
         shape = guide_legend(byrow = TRUE,
                              override.aes = list(size = 4)))
dev.off()
```

## Global Metrics

### Weighted Density

```{r}
# Convenience
common_theme = theme(
  axis.title.y = element_blank(), 
  axis.ticks.y = element_blank(),  
  plot.title = element_text(hjust = 0.5),   
  legend.position = "right",        
  legend.box = "vertical",
  legend.justification = "center"   
)

## Redundant network

ggWD = data.frame(
  True.Network = global_metrics[,1,"Weighted Density"],
  Redundant.Network = global_metrics[,2,"Weighted Density"],
  Redundant.Network.Without.Clone = global_metrics[,3,"Weighted Density"])

stacked_WD = stack(x = ggWD, select = c("True.Network", "Redundant.Network", "Redundant.Network.Without.Clone"))

# Basic density ridge plot

# ggplot(stacked_df, aes(x = values,
#                        y = ind,
#                        fill = ind)) +
#   geom_density_ridges(quantile_lines = TRUE,
#                       quantiles = c(0.025, 0.975),
#                       alpha = 0.7) +
#   theme_minimal()

# Quartile ridgeline plot
p1 = ggplot(stacked_WD, aes(x = values,
                       y = ind,
                       fill = factor(stat(quantile)))) +
  stat_density_ridges(geom = "density_ridges_gradient",
                             calc_ecdf = TRUE,
                             quantiles = 4,
                             quantile_lines = TRUE) + 
  scale_fill_viridis_d(name = "Quartiles") +
  scale_y_discrete(labels = c("True Network",
                              "Redundant Network",
                              "Redundant Network w/o Clone")) +
  scale_x_continuous(limits = c(0.1,.5)) +
  labs(x = NULL,
       y = "Network",
       title = "Weighted Density Ridgeline Plot") + 
  common_theme



# Jitter ridgeline plot
p3 = ggplot(stacked_WD, aes(x = values,
                       y = ind,
                       fill = ind)) +
  geom_density_ridges(aes(point_color = ind,
        point_fill = ind,
        point_shape = ind),
        alpha = .2,
        point_alpha = 1,
        jittered_points = TRUE) +
  scale_point_color_hue(l = 40) +
  scale_discrete_manual(aesthetics = "point_shape", values = c(21, 22, 23)) +
  scale_y_discrete(labels = c("True Network",
                              "Redundant Network",
                              "Redudant Network w/o Clone")) +
  scale_x_continuous(limits = c(0.1,.5)) +
  labs(x = NULL,
       y = "Network",
       title = "Weighted Density Ridgeline Plot") +
  common_theme +
  theme(legend.position = "none")

p3


## Random Network

ggWD.random = data.frame(
  True.Network = global_metrics_random[,1,"Weighted Density"],
  Random.Network = global_metrics_random[,2,"Weighted Density"],
  Random.Network.Without.Random = global_metrics_random[,3,"Weighted Density"])

stacked_WD_random = stack(x = ggWD.random, select = c("True.Network", "Random.Network", "Random.Network.Without.Random"))

# Quartile ridgeline plot
p2  = ggplot(stacked_WD_random, aes(x = values,
                       y = ind,
                       fill = factor(stat(quantile)))) +
  stat_density_ridges(geom = "density_ridges_gradient",
                             calc_ecdf = TRUE,
                             quantiles = 4,
                             quantile_lines = TRUE) + 
  scale_fill_viridis_d(name = "Quartiles") +
  scale_y_discrete(labels = c("True Network",
                              "Random Network",
                              "Random Network w/o additional node")) +
  scale_x_continuous(limits = c(0.1,.5)) +
  labs(x = "Weighted Density",
       y = "Network") +
  common_theme

# Jitter ridgeline plot

p4 = ggplot(stacked_WD_random, aes(x = values,
                       y = ind,
                       fill = ind)) +
  geom_density_ridges(aes(point_color = ind,
        point_fill = ind,
        point_shape = ind),
        alpha = .2,
        point_alpha = 1,
        jittered_points = TRUE) +
  scale_point_color_hue(l = 40) +
  scale_discrete_manual(aesthetics = "point_shape", values = c(21, 22, 23)) +
  scale_x_continuous(limits = c(0.1,.5)) +
  scale_y_discrete(labels = c("True Network",
                              "Random Network",
                              "Random Network w/o additional node")) +
  labs(x = "Weighted Density",
       y = "Network") +
  common_theme +
  theme(legend.position = "none")

```

### Patchwork Plots

```{r}
# Quartile
jpeg("/Users/abraham/Library/CloudStorage/Box-Box/Redundancy_Project/Output/Weighted Density Plot (Quartile).jpg",
     width= 12,
     height= 6,
     res=800,
     units="in")
p1/p2 +
  plot_layout(guides = "collect")
dev.off()

# Jitter
jpeg("/Users/abraham/Library/CloudStorage/Box-Box/Redundancy_Project/Output/Weighted Density Plot (Jitter).jpg",
     width= 12,
     height= 6,
     res=800,
     units="in")
p3/p4 + 
  plot_layout(guides = "collect")
dev.off()
```

### APL

```{r}

```

### Patchwork Plots

```{r}

```

# Final Simulation Plots

```{r}
data = readRDS("/Users/abraham/Library/CloudStorage/Box-Box/Redundancy_Project/R/Simulation Results/simulation.results.rds")


# Prepare data for plotting 
# First I will load packages
package.list = c("ggplot2", "tidyr", "ggridges",
                 "patchwork", "dplyr", "purrr", "stringr")

invisible(sapply(package.list, function(package){
  if(!require(package, character.only = TRUE)){
    install.packages(package, dependencies = TRUE)
  }
  library(package, character.only = TRUE)
}))

# Learn to subset properly from a list 
View(data) # To easily see each condition

# Extract an array (1st condition/first array)
dim(data[[1]]$local.metrics)[2]



compute.avg.diffs = function(array, node.names = NULL) {

  n.nodes = dim(array)[2]
  p = (n.nodes - 1) / 2

  if (p %% 1 != 0) {
    stop("Column structure is not (peripheral, redundant, clone/random)")
  }

  orig.idx = 1:p
  red.idx  = (p + 1):(2 * p)

  diffs = array[, red.idx, ] - array[, orig.idx, ]
  avg.diffs = apply(diffs, c(2, 3), mean, na.rm = TRUE)

  df = as.data.frame(avg.diffs)

  if (!is.null(node.names)) {
    if (length(node.names) != p) {
      stop("node_names length does not match number of original nodes")
    }
    rownames(df) = node.names
  }

  df
}



# SDs

compute.sd.diffs = function(array, node.names = NULL) {

  n.nodes = dim(array)[2]
  p = (n.nodes - 1) / 2

  if (p %% 1 != 0) {
    stop("Column structure is not (peripheral, redundant, clone/random)")
  }

  orig.idx = 1:p
  red.idx  = (p + 1):(2 * p)

  diffs = array[, red.idx, ] - array[, orig.idx, ]
  sd.diffs = apply(diffs, c(2, 3), sd, na.rm = TRUE)

  df = as.data.frame(sd.diffs)

  if (!is.null(node.names)) {
    if (length(node.names) != p) {
      stop("node_names length does not match number of original nodes")
    }
    rownames(df) = node.names
  }

  df
}

# mean results 

diff.results = lapply(data, function(cond) {

  df.local = compute.avg.diffs(cond$local.metrics)
  df.random = compute.avg.diffs(cond$local.metrics.random)

  list(
    condition = cond$condition,
    local     = df.local,
    random    = df.random
  )
})

# SDs

diff.results.sd = lapply(data, function(cond) {

  df.local = compute.sd.diffs(cond$local.metrics)
  df.random = compute.sd.diffs(cond$local.metrics.random)

  list(
    condition = cond$condition,
    local     = df.local,
    random    = df.random
  )
})


## Function to collapse peripheral nodes 1-9


# Function to manually do everything
collapse.peripherals = function(df){
  n = nrow(df)
# Get all peripheral nodes
  peripherals = 1:(n-1)
# Target node
  target = n
# Collapse all peripheral nodes into their mean and combine rows
  collapsed = rbind(
    colMeans(df[peripherals, , drop = FALSE]),
    df[target, , drop = F])
  rownames(collapsed) = c("Peripheral Nodes", "Target")
  collapsed
}


# Collapsed results for means

local.results.c = lapply(diff.results, function(x){
  x$local = collapse.peripherals(x$local)
  x$random = collapse.peripherals(x$random)
  x
})


# Collapsed results for sds

local.results.csd = lapply(diff.results.sd, function(x){
  x$local = collapse.peripherals(x$local)
  x$random = collapse.peripherals(x$random)
  x
})



```

```{r}
## Get ready for plotting 


df.ei = map_dfr(local.results.c, function(x){
  cond = x$condition
  df = x$local
  
  tibble(
    nv = cond$nv,
    sd = cond$sd,
    clone.loading = cond$clone.loading,
    
    `Peripheral Nodes` = df["Peripheral Nodes", "Expected Influence"],
    `Target` = df["Target", "Expected Influence"],
    `Target w/o Clone` = df["Target", "Expected Influence w/o Clone"]
  ) |> 
    pivot_longer(
      cols = c(`Peripheral Nodes`, `Target`,`Target w/o Clone`),
               names_to = "node.type",
               values_to ="expected.influence")
  
})

```

```{r}



df.metrics = map_dfr(local.results.c, function(x) {

  cond = x$condition
  df = x$local

  # identify base metric names (without " w/o Clone")
  metrics = unique(gsub(" w/o Clone", "", colnames(df)))

  map_dfr(metrics, function(m) {
    tibble(
      nv = cond$nv,
      sd = cond$sd,
      clone.loading = cond$clone.loading,
      metric = m,
      `Peripheral Nodes` = df["Peripheral Nodes", m],
      `Peripheral Nodes w/o Clone` = df["Peripheral Nodes",
                                        paste0(m, " w/o Clone")],
      `Target` = df["Target", m],
      `Target w/o Clone` = df["Target", paste0(m, " w/o Clone")]
    ) |>
      pivot_longer(
        cols = c(`Peripheral Nodes`, `Peripheral Nodes w/o Clone`,
                 `Target`, `Target w/o Clone`),
        names_to = "node.type",
        values_to = "value"
      )
  })
})


df.metrics.sd = map_dfr(local.results.csd, function(x) {

  cond = x$condition
  df = x$local

  # identify base metric names (without " w/o Clone")
  metrics = unique(gsub(" w/o Clone", "", colnames(df)))

  map_dfr(metrics, function(m) {
    tibble(
      nv = cond$nv,
      sd = cond$sd,
      clone.loading = cond$clone.loading,
      metric = m,
      `Peripheral Nodes` = df["Peripheral Nodes", m],
      `Peripheral Nodes w/o Clone` = df["Peripheral Nodes",
                                        paste0(m, " w/o Clone")],
      `Target` = df["Target", m],
      `Target w/o Clone` = df["Target", paste0(m, " w/o Clone")]
    ) |>
      pivot_longer(
        cols = c(`Peripheral Nodes`, `Peripheral Nodes w/o Clone`,
                 `Target`, `Target w/o Clone`),
        names_to = "node.type",
        values_to = "value"
      )
  })
})



```

## Clone loading = .9

### EI

```{r}


df.ei.09 = df.metrics |> 
  filter(clone.loading == .9 & metric == "Expected Influence")

df.sd = df.metrics.sd |> 
  filter(clone.loading == 0.9, metric == "Expected Influence") |>
  rename(sd_value = value)

df.plot = df.ei.09 |> 
  left_join(df.sd, by = c("nv", "sd", "clone.loading", "metric", "node.type"))
df.plot

ggplot(df.plot, aes(x = node.type,
                     y = value,
                     color = factor(nv),
                     group = interaction(node.type, nv))) +
  geom_point(size = 3.5, aes(shape = node.type)) +
  scale_shape_manual(
  values = c(
    "Peripheral Nodes" = 18,
    "Peripheral Nodes w/o Clone" = 15,
    "Target" = 16,            
    "Target w/o Clone" = 17)) +
  facet_wrap(~ sd,
             nrow = 3,
             labeller = labeller(sd = function(x) paste0("SD = ", x))) +
geom_errorbar(aes(ymin = value - sd_value / sqrt(1000),
                    ymax = value + sd_value / sqrt(1000)),
                width = 0.1, color = "black", linewidth = 0.3) +
  labs(
    x = "Node Type",
    y = "Expected Influence",
    color = "Network Size"
  ) +
  coord_cartesian(ylim = c(-0.5, 0.5)) +
  guides(shape = "none") + 
  theme_light() +
  theme(
    strip.text = element_text(face = "bold.italic"),
    axis.text.x = element_text(angle = 20, hjust = 1))

```

### Strength

```{r}
df.s.09 = df.metrics |> 
  filter(clone.loading == .9 & metric == "Strength")

df.s.sd = df.metrics.sd |> 
  filter(clone.loading == 0.9, metric == "Strength") |>
  rename(sd_value = value)

df.plot.s = df.s.09 |> 
  left_join(df.s.sd, by = c("nv", "sd", "clone.loading", "metric", "node.type"))


ggplot(df.plot.s, aes(x = node.type,
                     y = value,
                     color = factor(nv),
                     group = interaction(node.type, nv))) +
  geom_point(size = 3.5, aes(shape = node.type)) +
  scale_shape_manual(
  values = c(
    "Peripheral Nodes" = 18,
    "Peripheral Nodes w/o Clone" = 15,
    "Target" = 16,            
    "Target w/o Clone" = 17)) +
  facet_wrap(~ sd,
             nrow = 3,
             labeller = labeller(sd = function(x) paste0("SD = ", x))) +
geom_errorbar(aes(ymin = value - sd_value / sqrt(1000),
                    ymax = value + sd_value / sqrt(1000)),
                width = 0.1, color = "black", linewidth = 0.3) +
  labs(
    x = "Node Type",
    y = "Strength",
    color = "Network Size"
  ) +
  coord_cartesian(ylim = c(-1.5, 1.5)) +
  guides(shape = "none") + 
  theme_light() +
  theme(
    strip.text = element_text(face = "bold.italic"),
    axis.text.x = element_text(angle = 20, hjust = 1))
```

### Closeness

```{r}
df.c.09 = df.metrics |> 
  filter(clone.loading == .9 & metric == "Closeness")

df.c.sd = df.metrics.sd |> 
  filter(clone.loading == 0.9, metric == "Closeness") |>
  rename(sd_value = value)

df.plot.c = df.c.09 |> 
  left_join(df.c.sd, by = c("nv", "sd", "clone.loading", "metric", "node.type"))


ggplot(df.plot.c, aes(x = node.type,
                     y = value,
                     color = factor(nv),
                     group = interaction(node.type, nv))) +
  geom_point(size = 3.5, aes(shape = node.type)) +
  scale_shape_manual(
  values = c(
    "Peripheral Nodes" = 18,
    "Peripheral Nodes w/o Clone" = 15,
    "Target" = 16,            
    "Target w/o Clone" = 17)) +
  facet_wrap(~ sd,
             nrow = 3,
             labeller = labeller(sd = function(x) paste0("SD = ", x))) +
geom_errorbar(aes(ymin = value - sd_value / sqrt(1000),
                    ymax = value + sd_value / sqrt(1000)),
                width = 0.1, color = "black", linewidth = 0.3) +
  labs(
    x = "Node Type",
    y = "Closeness",
    color = "Network Size"
  ) +
  coord_cartesian(ylim = c(-.15, .15)) +
  guides(shape = "none") + 
  theme_light() +
  theme(
    strip.text = element_text(face = "bold.italic"),
    axis.text.x = element_text(angle = 20, hjust = 1))
```

### Betweenness

```{r}
df.b.09 = df.metrics |> 
  filter(clone.loading == .9 & metric == "Betweenness")

df.b.sd = df.metrics.sd |> 
  filter(clone.loading == 0.9, metric == "Betweenness") |>
  rename(sd_value = value)

df.plot.b = df.b.09 |> 
  left_join(df.b.sd, by = c("nv", "sd", "clone.loading", "metric", "node.type"))


ggplot(df.plot.b, aes(x = node.type,
                     y = value,
                     color = factor(nv),
                     group = interaction(node.type, nv))) +
  geom_point(size = 3.5, aes(shape = node.type)) +
  scale_shape_manual(
  values = c(
    "Peripheral Nodes" = 18,
    "Peripheral Nodes w/o Clone" = 15,
    "Target" = 16,            
    "Target w/o Clone" = 17)) +
  facet_wrap(~ sd,
             nrow = 3,
             labeller = labeller(sd = function(x) paste0("SD = ", x))) +
geom_errorbar(aes(ymin = value - sd_value / sqrt(1000),
                    ymax = value + sd_value / sqrt(1000)),
                width = 0.1, color = "black", linewidth = 0.3) +
  labs(
    x = "Node Type",
    y = "Betweenness",
    color = "Network Size"
  ) +
  coord_cartesian(ylim = c(-10, 10)) +
  scale_y_continuous(breaks = c(-10, -5, 0, 5, 10)) +
  guides(shape = "none") + 
  theme_light() +
  theme(
    strip.text = element_text(face = "bold.italic"),
    axis.text.x = element_text(angle = 20, hjust = 1))
```

## Clone Loading = .9 and .7

### EI

```{r}

df.ei.loadings = df.metrics |> 
  filter(clone.loading %in% c(.9, .7) & metric == "Expected Influence")

df.ei.loadings.sd = df.metrics.sd |> 
  filter(clone.loading %in% c(.9, .7), metric == "Expected Influence") |>  rename(sd_value = value)

df.plot.ei = df.ei.loadings |> 
  left_join(df.ei.loadings.sd, by = c("nv", "sd", "clone.loading", "metric", "node.type"))


ggplot(df.plot.ei, aes(x = node.type,
                     y = value,
                     color = factor(nv),
                     group = interaction(node.type, nv))) +
  geom_point(size = 3.5, aes(shape = node.type)) +
  scale_shape_manual(
  values = c(
    "Peripheral Nodes" = 18,
    "Peripheral Nodes w/o Clone" = 15,
    "Target" = 16,            
    "Target w/o Clone" = 17)) +
  facet_wrap(~ sd + clone.loading,
             nrow = 3,
             labeller = labeller(sd = function(x) paste0("SD = ", x))) +
geom_errorbar(aes(ymin = value - sd_value / sqrt(1000),
                    ymax = value + sd_value / sqrt(1000)),
                width = 0.1, color = "black", linewidth = 0.3) +
  labs(
    x = "Node Type",
    y = "Expected Influence",
    color = "Network Size"
  ) +
  coord_cartesian(ylim = c(-0.5, 0.5)) +
  guides(shape = "none") + 
  theme_light() +
  theme(
    strip.text = element_text(face = "bold.italic"),
    axis.text.x = element_text(angle = 20, hjust = 1))



```

### Strength

```{r}
df.s.loadings = df.metrics |> 
  filter(clone.loading %in% c(.9, .7) & metric == "Strength")

df.s.loadings.sd = df.metrics.sd |> 
  filter(clone.loading %in% c(.9, .7), metric == "Strength") |> 
  rename(sd_value = value)

df.plot.s = df.s.loadings |> 
  left_join(df.s.loadings.sd, by = c("nv", "sd", "clone.loading", "metric", "node.type"))


ggplot(df.plot.s, aes(x = node.type,
                     y = value,
                     color = factor(nv),
                     group = interaction(node.type, nv))) +
  geom_point(size = 3.5, aes(shape = node.type)) +
  scale_shape_manual(
  values = c(
    "Peripheral Nodes" = 18,
    "Peripheral Nodes w/o Clone" = 15,
    "Target" = 16,            
    "Target w/o Clone" = 17)) +
  facet_wrap(~ sd + clone.loading,
             nrow = 3,
             labeller = labeller(sd = function(x) paste0("SD = ", x))) +
geom_errorbar(aes(ymin = value - sd_value / sqrt(1000),
                    ymax = value + sd_value / sqrt(1000)),
                width = 0.1, color = "black", linewidth = 0.3) +
  labs(
    x = "Node Type",
    y = "Strength",
    color = "Network Size"
  ) +
  coord_cartesian(ylim = c(-1.5, 1.5)) +
  guides(shape = "none") + 
  theme_light() +
  theme(
    strip.text = element_text(face = "bold.italic"),
    axis.text.x = element_text(angle = 20, hjust = 1))
```

### Closeness

```{r}
df.c.loadings = df.metrics |> 
  filter(clone.loading %in% c(.9, .7) & metric == "Closeness")

df.c.loadings.sd = df.metrics.sd |> 
  filter(clone.loading %in% c(.9, .7), metric == "Closeness") |> 
  rename(sd_value = value)

df.plot.c = df.c.loadings |> 
  left_join(df.c.loadings.sd, by = c("nv", "sd", "clone.loading", "metric", "node.type"))


ggplot(df.plot.c, aes(x = node.type,
                     y = value,
                     color = factor(nv),
                     group = interaction(node.type, nv))) +
  geom_point(size = 3.5, aes(shape = node.type)) +
  scale_shape_manual(
  values = c(
    "Peripheral Nodes" = 18,
    "Peripheral Nodes w/o Clone" = 15,
    "Target" = 16,            
    "Target w/o Clone" = 17)) +
  facet_wrap(~ sd + clone.loading,
             nrow = 3,
             labeller = labeller(sd = function(x) paste0("SD = ", x))) +
geom_errorbar(aes(ymin = value - sd_value / sqrt(1000),
                    ymax = value + sd_value / sqrt(1000)),
                width = 0.1, color = "black", linewidth = 0.3) +
  labs(
    x = "Node Type",
    y = "Closeness",
    color = "Network Size"
  ) +
  coord_cartesian(ylim = c(-.15, .15)) +
  guides(shape = "none") + 
  theme_light() +
  theme(
    strip.text = element_text(face = "bold.italic"),
    axis.text.x = element_text(angle = 20, hjust = 1))
```

### Betweenness

```{r}
df.b.loadings = df.metrics |> 
  filter(clone.loading %in% c(.9, .7) & metric == "Betweenness")

df.b.loadings.sd = df.metrics.sd |> 
  filter(clone.loading %in% c(.9, .7), metric == "Betweenness") |> 
  rename(sd_value = value)

df.plot.b = df.b.loadings |> 
  left_join(df.b.loadings.sd, by = c("nv", "sd", "clone.loading", "metric", "node.type"))


ggplot(df.plot.b, aes(x = node.type,
                     y = value,
                     color = factor(nv),
                     group = interaction(node.type, nv))) +
  geom_point(size = 3.5, aes(shape = node.type)) +
  scale_shape_manual(
  values = c(
    "Peripheral Nodes" = 18,
    "Peripheral Nodes w/o Clone" = 15,
    "Target" = 16,            
    "Target w/o Clone" = 17)) +
  facet_wrap(~ sd + clone.loading,
             nrow = 3,
             labeller = labeller(sd = function(x) paste0("SD = ", x))) +
geom_errorbar(aes(ymin = value - sd_value / sqrt(1000),
                    ymax = value + sd_value / sqrt(1000)),
                width = 0.1, color = "black", linewidth = 0.3) +
  labs(
    x = "Node Type",
    y = "Betweenness",
    color = "Network Size"
  ) +
  coord_cartesian(ylim = c(-17, 17)) +
  scale_y_continuous(breaks = c(-17, -10, -5, 0, 5, 10, 17)) +
  guides(shape = "none") + 
  theme_light() +
  theme(
    strip.text = element_text(face = "bold.italic"),
    axis.text.x = element_text(angle = 20, hjust = 1))
```

## Random Network, Loading = .9

```{r}
# Random Mean results 
df.metrics = map_dfr(local.results.c, function(x) {

  cond = x$condition
  df = x$local

  # identify base metric names (without " w/o Clone")
  metrics = unique(gsub(" w/o Clone", "", colnames(df)))

  map_dfr(metrics, function(m) {
    tibble(
      nv = cond$nv,
      sd = cond$sd,
      clone.loading = cond$clone.loading,
      metric = m,
      `Peripheral Nodes` = df["Peripheral Nodes", m],
      `Peripheral Nodes w/o Clone` = df["Peripheral Nodes",
                                        paste0(m, " w/o Clone")],
      `Target` = df["Target", m],
      `Target w/o Clone` = df["Target", paste0(m, " w/o Clone")]
    ) |>
      pivot_longer(
        cols = c(`Peripheral Nodes`, `Peripheral Nodes w/o Clone`,
                 `Target`, `Target w/o Clone`),
        names_to = "node.type",
        values_to = "value"
      )
  })
})
```


# Global Metrics

## Weighted Density C1

```{r}
# Subset each array for global metrics

global.metrics = lapply(data, function(x){
  list(
   condition =  x[[1]],
   global = x[[3]])
})

wd.1 = as.data.frame(global.metrics[[1]]$global[,,"Weighted Density"])


stacked.wd.1 = stack(x = wd.1, select = c("True Network", "Redundant Network", "Redundant Network w/o Clone"))




common_theme = theme(
  axis.title.y = element_blank(), 
  axis.ticks.y = element_blank(),  
  plot.title = element_text(hjust = 0.5),   
  legend.position = "right",        
  legend.box = "vertical",
  legend.justification = "center"   
)

# Jitter ridgeline plot
p1 = ggplot(stacked.wd.1, aes(
  x = values,
  y = ind,
  fill = ind)) +
  geom_density_ridges(aes(point_color = ind,
        point_fill = ind,
        point_shape = ind),
        alpha = .2,
        point_alpha = 1,
        jittered_points = TRUE) +
  scale_point_color_hue(l = 40) +
  scale_discrete_manual(aesthetics = "point_shape", values = c(21, 22, 23)) +
  scale_y_discrete(labels = c("True Network",
                              "Redundant Network",
                              "Redudant Network w/o Clone")) +
  scale_x_continuous(limits = c(0.1,.3)) +
  labs(x = NULL,
       y = "Network",
       title = "Weighted Density Ridgeline Plot") +
  common_theme + 
  theme(legend.position = "none")


```

## APL C1

```{r}


apl.1 = as.data.frame(global.metrics[[1]]$global[,,"APL"])


stacked.apl.1 = stack(x = apl.1, select = c("True Network", "Redundant Network", "Redundant Network w/o Clone"))


min(stacked.apl.1$values)

common_theme = theme(
  axis.title.y = element_blank(), 
  axis.ticks.y = element_blank(),  
  plot.title = element_text(hjust = 0.5),   
  legend.position = "right",        
  legend.box = "vertical",
  legend.justification = "center"   
)

# Jitter ridgeline plot
p2 = ggplot(stacked.apl.1, aes(
  x = values,
  y = ind,
  fill = ind)) +
  geom_density_ridges(aes(point_color = ind,
        point_fill = ind,
        point_shape = ind),
        alpha = .2,
        point_alpha = 1,
        jittered_points = TRUE) +
  scale_point_color_hue(l = 40) +
  scale_discrete_manual(aesthetics = "point_shape", values = c(21, 22, 23)) +
  scale_y_discrete(labels = c("True Network",
                              "Redundant Network",
                              "Redudant Network w/o Clone")) +
  scale_x_continuous(limits = c(0,12)) +
  labs(x = NULL,
       y = "Network",
       title = "APL Ridgeline Plot") +
  common_theme + 
  theme(legend.position = "none")
p2
```


## Weighted Density C2

```{r}
wd.2 = as.data.frame(global.metrics[[2]]$global[,,"Weighted Density"])


stacked.wd.2 = stack(x = wd.2, select = c("True Network", "Redundant Network", "Redundant Network w/o Clone"))



# Jitter ridgeline plot
p3 = ggplot(stacked.wd.2, aes(
  x = values,
  y = ind,
  fill = ind)) +
  geom_density_ridges(aes(point_color = ind,
        point_fill = ind,
        point_shape = ind),
        alpha = .2,
        point_alpha = 1,
        jittered_points = TRUE) +
  scale_point_color_hue(l = 40) +
  scale_discrete_manual(aesthetics = "point_shape", values = c(21, 22, 23)) +
  scale_y_discrete(labels = c("True Network",
                              "Redundant Network",
                              "Redudant Network w/o Clone")) +
  scale_x_continuous(limits = c(0.1,.25)) +
  labs(x = NULL,
       y = "Network",
       title = "Weighted Density Ridgeline Plot") +
  common_theme + 
  theme(legend.position = "none")

```

## APL C2

```{r}
apl.2 = as.data.frame(global.metrics[[2]]$global[,,"APL"])


stacked.apl.2 = stack(x = apl.2, select = c("True Network", "Redundant Network", "Redundant Network w/o Clone"))


max(stacked.apl.2$values)

# Jitter ridgeline plot
p4 = ggplot(stacked.apl.2, aes(
  x = values,
  y = ind,
  fill = ind)) +
  geom_density_ridges(aes(point_color = ind,
        point_fill = ind,
        point_shape = ind),
        alpha = .2,
        point_alpha = 1,
        jittered_points = TRUE) +
  scale_point_color_hue(l = 40) +
  scale_discrete_manual(aesthetics = "point_shape", values = c(21, 22, 23)) +
  scale_y_discrete(labels = c("True Network",
                              "Redundant Network",
                              "Redudant Network w/o Clone")) +
  scale_x_continuous(limits = c(4,9)) +
  labs(x = NULL,
       y = "Network",
       title = "APL Ridgeline Plot") +
  common_theme + 
  theme(legend.position = "none")

```


## Weighted Density C5


```{r}
wd.5 = as.data.frame(global.metrics[[5]]$global[,,"Weighted Density"])


stacked.wd.5 = stack(x = wd.5, select = c("True Network", "Redundant Network", "Redundant Network w/o Clone"))



# Jitter ridgeline plot
p7 = ggplot(stacked.wd.5, aes(
  x = values,
  y = ind,
  fill = ind)) +
  geom_density_ridges(aes(point_color = ind,
        point_fill = ind,
        point_shape = ind),
        alpha = .2,
        point_alpha = 1,
        jittered_points = TRUE) +
  scale_point_color_hue(l = 40) +
  scale_discrete_manual(aesthetics = "point_shape", values = c(21, 22, 23)) +
  scale_y_discrete(labels = c("True Network",
                              "Redundant Network",
                              "Redudant Network w/o Clone")) +
  scale_x_continuous(limits = c(0.1,.3)) +
  labs(x = NULL,
       y = "Network",
       title = "Weighted Density Ridgeline Plot C5") +
  common_theme + 
  theme(legend.position = "none")
p7

```

## APL C5

```{r}
apl.5 = as.data.frame(global.metrics[[5]]$global[,,"APL"])


stacked.apl.5 = stack(x = apl.5, select = c("True Network", "Redundant Network", "Redundant Network w/o Clone"))


min(stacked.apl.5$values)

# Jitter ridgeline plot
p8 = ggplot(stacked.apl.5, aes(
  x = values,
  y = ind,
  fill = ind)) +
  geom_density_ridges(aes(point_color = ind,
        point_fill = ind,
        point_shape = ind),
        alpha = .2,
        point_alpha = 1,
        jittered_points = TRUE) +
  scale_point_color_hue(l = 40) +
  scale_discrete_manual(aesthetics = "point_shape", values = c(21, 22, 23)) +
  scale_y_discrete(labels = c("True Network",
                              "Redundant Network",
                              "Redudant Network w/o Clone")) +
  scale_x_continuous(limits = c(3.5,8)) +
  labs(x = NULL,
       y = "Network",
       title = "APL Ridgeline Plot") +
  common_theme + 
  theme(legend.position = "none")
p8

```




